Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-24 demystify.tex
Updates from Overleaf

\chapterinfo{Yes, definitely.  CS PhD study in the US is often fully funded and admission into good universities in the US is not any harder than in other countries.}

@@

\paragraph{Not any harder than other countries} First, applying to a good US university \emph{should not} be any harder than at schools in other countries. It might even be more flexible since CS PhD in the US \emph{do not} require having an MS or a research topic, proposal, or adviser in advance (\autoref{sec:non-us-differences} compares CS PhD study in the US to other countries). It doesn't even require having a CS background (\autoref{sec:non-stem}).
If you believe you have a chance in other countries, e.g., South Korea, Singapore, Germany, UK, Japan, and Australia, then you will surely have a chance in the US as well.

@@

\paragraph{Core CS topics} Common CS knowledge that you should know are:
\begin{itemize}
  \item Programming Foundation (e.g., programming concepts in some modern languages)
  \item Discrete Math (e.g., logic, set theory, proof techniques)
  \item Data Structures and Algorithms (e.g., linked lists, trees, sorting, searching)
  \item Computer OS or Systems (e.g., memory management, file systems, processes)
\end{itemize}

>>>>

\chapterinfo{Yes, definitely.  CS PhD study in the US is often \textbf{fully funded} and admission into good universities in the US is \textbf{not} any harder than in other countries.}

@@

\paragraph*{Not any harder than other countries} First, applying to a good US university \emph{should not} be any harder than at schools in other countries. It might even be more flexible since CS PhD in the US \emph{do not} require having an MS or a research topic, proposal, or adviser in advance (\autoref{sec:non-us-differences} compares CS PhD study in the US to other countries). It doesn't even require having a CS background (\autoref{sec:non-stem}).
If you believe you have a chance in other countries, e.g., South Korea, Singapore, Germany, UK, Japan, and Australia, then you will surely have a chance in the US as well.

@@

\paragraph*{Core CS topics} Common CS knowledge that you should know are:

\begin{itemize}
  \item Programming Foundation (e.g., programming concepts in some modern languages)
  \item Discrete Math (e.g., logic, set theory, proof techniques)
  \item Data Structures and Algorithms (e.g., linked lists, trees, sorting, searching)
  \item Computer OS or Systems (e.g., memory management, file systems, processes)
\end{itemize}
